Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-02 draft.tex
small stuff
tft changes

The operad of little $n$-disks

\brian{main thrust is to interpret this in terms of the BV / BD formalism}

Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.

\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
\brian{as a corollary butson-yoo}

@@

\brian{Review interpretation of the center as a swiss cheese algebra context of Deligne conjecture}

\begin{prp}
For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times [0,1)$.
\end{prp}

>>>>

Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.

The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
manifold with boundary.

We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}. 
Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.

In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.

%Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.

\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
\brian{as a corollary butson-yoo}
\brian{main thrust is to interpret this in terms of the BV / BD formalism}

@@

The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
There is a similar operadic picture which encodes $E_{n+1}$-algebras together with their left-modules. 
The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.

An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is a left $B$-module. 
Indeed, if one restricts to the ``disk" colors we recover the data of $B$. 
The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $A$ on $B$.

Given an $E_n$-algebra $A$ we know that $E_n$-center $\fZ_n(A)$ has the structure of an $E_{n+1}$ algebra.
Moreover, the pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair.
This universality is a conjecture of \cite{Kontsevich} which was later made precise and proved in \cite{Thomas, Tamarkin, Dolgushev, jnkf others?}. 
One consequence of this \brian{universal property}

Abstractly, an algebra over the $(n+1)$-dimensional Swiss cheese operad can be modeled as a {\em constructible} factorization algebra on the upper half space $\HH^{n+1}$. 
Concretely, this is the data of (1) a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$, (2) a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$, (3) together with natural \brian{finish}

We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
Combining these descriptions we obtain the following.

\begin{prp}
For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
\end{prp}

\begin{proof}[Proof sketch]
In the bulk manifold $M \times \RR_{>0}$ we place the 
\end{proof}
